### 2016-11-28 local-capability-machine.tex
added comment

\subsection*{Semantics}
Assume a $\decode$ function that decodes words to instructions:
\begin{align*}
\decode &:\Words \fun \Instrs
\end{align*}
Assume an $\encodePerm$, $\encodeLoc$, and $\encodePermPair$ function that encodes a permissions, locality, and permission pair, respectively, as an integer:
\begin{align*}
\encodePerm &: \Perms \fun \ints \\
\encodeLoc &: \Globals \fun \ints \\
\encodePermPair &: (\Perms \times \Globals) \fun \ints \\
\end{align*}
Further, assume an inverse function, $\decodePermPair{}$, that decodes permissions
\[
  \decodePermPair{} : \ints \fun (\Perms \times \Globals)
\]
\begin{align*}
  \Phi & \rightarrow \sem{\decode(\memheap(\addr))}(\Phi) & &                                   
                                                              \arraycolsep=0pt
                                                              \begin{array}{l}
                                                                \text{if $\memreg(\pcreg) = \stdcap$}\\
                                                                \quad\text{and $\start \leq \addr \leq \addrend$}\\
                                                                \quad\text{and $\perm \in \{ \exec,\rwx, \rwlx \}$ }
                                                              \end{array}\\
\Phi & \rightarrow \failed                                 & & \text{otherwise}
\end{align*}

>>>>

\subsection*{Semantics}
Assume a $\decode$ function that decodes words to instructions:
\decode &:\Words \fun \Instrs
Assume an $\encodePerm$, $\encodeLoc$, and $\encodePermPair$ function that encodes a permissions, locality, and permission pair, respectively, as an integer:
\encodePerm &: \Perms \fun \ints \\
\encodeLoc &: \Globals \fun \ints \\
\encodePermPair &: (\Perms \times \Globals) \fun \ints \\
Further, assume an inverse function, $\decodePermPair{}$, that decodes permissions
  \decodePermPair{} : \ints \fun (\Perms \times \Globals)
  \Phi & \rightarrow \sem{\decode(\memheap(\addr))}(\Phi) & &                                   
                                                              \begin{array}{l}
                                                                \quad\text{and $\start \leq \addr \leq \addrend$}\\
                                                                \quad\text{and $\perm \in \{ \exec,\rwx, \rwlx \}$ }
\Phi & \rightarrow \failed                                 & & \text{otherwise}
\lau{With respect to our talk about whether the upper bound should be included in the range of authority or not, I have found one example where it would work better when the upper-bound is not included. If we have a stack and call and want to pass the empty part on, then if the unused part of the stack is 0 cells, then we cannot pass anything that ``looks like a stack''.}
